Solving Collective Spin Hamiltonians with Decoherence

### 2018-09-12 soc_squeezing/cumulant_expansions.tex
add text explaining transformation of spin operators for TAT protocol

\section{One-axis twisting revisited}

>>>>

\section{Decoherence in the two-axis twisting protocols}

In the case of squeezing through spin-orbit coupling with the Sr-87
optical lattice clock, the primary form of decoherence is through
decay of individual spins, i.e.~with jump operators $\sigma_-^{(j)}$.
The two axis twisting Hamiltonians $H_{\t{TAT}}^{\z,\y}$ and
$H_{\t{TAT}}^{\z,\y}$, however, are actually realized in a rotating
frame, which implies that we must transform these jump operators
appropriately.  Specifically, the TAT protocol begins with a
time-dependent transverse-field Hamiltonian
\begin{align}
  H = \chi S_\z^2 + \Omega\p{t} S_\x,
  &&
  \Omega\p{t} = \beta\omega\cos\p{\omega t} S_\x,
\end{align}
where $\beta$ is the modulation index of the driving field, and the
drive frequency $\omega\gg N\chi$.  Moving into the rotating frame of
$\Omega\p{t}S_\x$ subtracts this term from the Hamiltonian, and
transforms operators $\O$ as
\begin{align}
  \O \to U\p{t}^\dag \O U\p{t},
  &&
  U\p{t} \equiv \exp\p{-i\int_0^t\d\tau~\Omega\p{\tau}S_\x}
  = \exp\sp{-i\beta\sin\p{\omega t}S_\x},
\end{align}
In particular, the operators $\tilde S_\pm\equiv-S_\z\pm iS_\y$
transform as
\begin{align}
  \tilde S_\pm
  \to U^\dag \tilde S_\pm U
  = e^{\pm i\beta\sin\p{\omega t}} \tilde S_\pm.
\end{align}
For large drive frequencies $\omega$, we can generally make a secular
approximation to say
\begin{align}
  e^{\pm i\beta\sin\p{\omega t}}
  = \sum_{n=-\infty}^\infty J_n\p{\pm\beta} e^{in\omega t}
  \approx J_0\p{\pm\beta} = J_0\p{\beta},
\end{align}
where $J_0$ is the zero-order Bessel function of the first kind.
Expanding $S_\z^2=\f14\p{\tilde S_++\tilde S_-}^2$, one can thus work
out that the effective Hamiltonian in the rotating frame of the drive
is
\begin{align}
  H_{\t{eff}}
  \approx \f{\chi}{2} \p{\sp{J_0\p{2\beta}+1} S_\z^2
  - \sp{J_0\p{2\beta}-1} S_\y^2},
\end{align}
where choosing $\beta$ such that $J_0\p{2\beta}=\pm1/3$ will give us
$H_{\t{TAT}}^{\z,\y}$ or $H_{\t{TAT}}^{\y,\x}$ up to irrelevant terms.
In a similar spirit, one can work out that
\begin{align}
  \tilde\sigma_\pm^{(j)}
  \equiv \f12\p{-\sigma_\z^{(j)}\pm i\sigma_\y^{(j)}}
  \to U^\dag \tilde\sigma_\pm^{(j)} U
  = e^{\pm i\beta\sin\p{\omega t}} \tilde\sigma_\pm^{(j)}
  \approx J_0\p{\beta} \tilde\sigma_\pm^{(j)},
\end{align}
which implies
\begin{align}
  \sigma_\z^{(j)} \to J_0\p{\beta} \sigma_\z^{(j)},
  &&
  \sigma_\pm^{(j)}
  \to \f12\sp{1 \pm J_0\p{\beta}} \sigma_+^{(j)}
  + \f12\sp{1 \mp J_0\p{\beta}} \sigma_-^{(j)}.
\end{align}
The TAT protocol about $\p{\z,\y}$ requires
\begin{align}
  J_0\p{2\beta} = 1/3
  \implies \beta \approx 0.906
  \implies J_0\p{\beta} \approx 0.805,
\end{align}
while the TAT protocol about $\p{\y,\x}$ requires
\begin{align}
  J_0\p{2\beta} = -1/3
  \implies
  \begin{cases}
    \beta \approx 1.63
    \implies J_0\p{\beta} \approx 0.440, \\
    \beta \approx 2.22
    \implies J_0\p{\beta} \approx 0.099.
  \end{cases}
\end{align}
